A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-12-17 article/02_Materials_and_Methods.Rmd
decided to split the map figure

7. Manually defining a rectangular (EPSG:102013) research area with sufficient information in Central-, Northern and Northwestern Europe based on perceived spatial date distribution (Figure \ref{map} A).

@@

11. Defining macro regions to observe the development of *burial type* and *burial construction* within sensible geographical and cultural units that are appropriate to the amount of available data. The regions are circular and were delimited semi-automatically by creating a regular grid in accordance to main cultural-historical regions of the European Bronze Age (**citation**). The regions have a radius of 240km and overlap slightly (Figure \ref{map} B). That means some graves are counted towards not just one but two regions.

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/map.jpeg}
\caption{\label{map}This is a figure.}
\end{figure}

@@

Defining a measure of spatial distance for the above established main units of observation, the macro regions, is only possible in a highly simplified way. A continuous distance measure can't be employed, but it's possible to distinguish ordinal distance classes. For the eight regions four different categories of spatial distance were defined (Figure \ref{map} C). The test for correlation between spatial and cultural distance works similar to the one between the two cultural distances above, except that the Mantel test has to be applied with Spearman's rank correlation coefficient [@spearmanProofMeasurementAssociation1904] here, because of the difference in the data level of measurements. The test result are listed in Table \ref{tab:distanceandcorrelationtable*}.

>>>>

7. Manually defining a rectangular (EPSG:102013) research area with sufficient information in Central-, Northern and Northwestern Europe based on perceived spatial date distribution (Figure \ref{map_graves}).

@@

11. Defining macro regions to observe the development of *burial type* and *burial construction* within sensible geographical and cultural units that are appropriate to the amount of available data. The regions are circular and were delimited semi-automatically by creating a regular grid in accordance to main cultural-historical regions of the European Bronze Age (**citation**). The regions have a radius of 240km and overlap slightly (Figure \ref{map_regions} A). That means some graves are counted towards not just one but two regions.

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/map_graves.jpeg}
\caption{\label{map_graves}This is a figure.}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{../analysis/figures/map_regions.jpeg}
\caption{\label{map_regions}This is a figure.}
\end{figure}

@@

Defining a measure of spatial distance for the above established main units of observation, the macro regions, is only possible in a highly simplified way. A continuous distance measure can't be employed, but it's possible to distinguish ordinal distance classes. For the eight regions four different categories of spatial distance were defined (Figure \ref{map_regions} B). The test for correlation between spatial and cultural distance works similar to the one between the two cultural distances above, except that the Mantel test has to be applied with Spearman's rank correlation coefficient [@spearmanProofMeasurementAssociation1904] here, because of the difference in the data level of measurements. The test result are listed in Table \ref{tab:distanceandcorrelationtable*}.

### 2018-12-17 article/03_Results.Rmd
decided to split the map figure

`r a("Southeastern Central Europe")`^[Amount of graves in Radon-B for this region.]:
The artificial study region *Southeastern Central Europe* comprises the eastern part of Austria (Upper Austria, Lower Austria, Styria, Burgenland), the northwest of Hungary, Western Slovakia, Moravia and large parts of Bohemia (Figure \ref{map} B). The density of ^14^C data on graves in Radon-B is low -- individual dates are available from the various regions, but large areas are without evidence. Diachronically the amount of data is consistently low and reaches a minimum in the Middle Bronze Age. While for the *burial type* variable a constant flow of information is given, the number of graves without information on *burial construction* increases in the Late Bronze Age to such an extent that no meaningful overview can be derived. The comparison with archaeological observations is complicated by the fact that the region intersects diverse geographical and cultural areas. In the southeast of Central Europe, cremation and bodily burial already existed side by side in the Early Bronze Age, and the local tradition remained stable in this respect also due to the expansion of the burial mound tradition in the Middle Bronze Age -- with a slight overall increase in cremation graves. The Urnfield period brought the transition to the absolute dominance of cremation burial. The development of the *burial type* variable in the Radon-B proxy shows this development correctly. The information from ^14^C data on *burial construction* correctly traces the relevance of flat burials in the Early Bronze Age, but the latter are then overemphasized in the Middle Bronze Age compared to the construction of burial mounds. In the Late Bronze Age, burials on flat burial grounds were frequent, although burial mounds of the Tumulus Culture were also further documented. This impact cannot be correctly deduced from Radon-B -- certainly due to the small amount of data [@lubosCzechLandsAustria2013; @markovaSlovakiaHungary2013]. \newline

>>>>

`r a("Southeastern Central Europe")`^[Amount of graves in Radon-B for this region.]:
The artificial study region *Southeastern Central Europe* comprises the eastern part of Austria (Upper Austria, Lower Austria, Styria, Burgenland), the northwest of Hungary, Western Slovakia, Moravia and large parts of Bohemia (Figure \ref{map_regions} A). The density of ^14^C data on graves in Radon-B is low -- individual dates are available from the various regions, but large areas are without evidence. Diachronically the amount of data is consistently low and reaches a minimum in the Middle Bronze Age. While for the *burial type* variable a constant flow of information is given, the number of graves without information on *burial construction* increases in the Late Bronze Age to such an extent that no meaningful overview can be derived. The comparison with archaeological observations is complicated by the fact that the region intersects diverse geographical and cultural areas. In the southeast of Central Europe, cremation and bodily burial already existed side by side in the Early Bronze Age, and the local tradition remained stable in this respect also due to the expansion of the burial mound tradition in the Middle Bronze Age -- with a slight overall increase in cremation graves. The Urnfield period brought the transition to the absolute dominance of cremation burial. The development of the *burial type* variable in the Radon-B proxy shows this development correctly. The information from ^14^C data on *burial construction* correctly traces the relevance of flat burials in the Early Bronze Age, but the latter are then overemphasized in the Middle Bronze Age compared to the construction of burial mounds. In the Late Bronze Age, burials on flat burial grounds were frequent, although burial mounds of the Tumulus Culture were also further documented. This impact cannot be correctly deduced from Radon-B -- certainly due to the small amount of data [@lubosCzechLandsAustria2013; @markovaSlovakiaHungary2013]. \newline
